### 2023-05-04 README.Rmd
Minor documentation changes
Updated docs

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://CRAN.R-project.org) with:

@@

And the development version of the `fasano.franceschini.test` package from [GitHub](https://github.com/) with:

>>>>

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://cran.r-project.org/web/packages/fasano.franceschini.test/index.html) with:

@@

The development version of the `fasano.franceschini.test` package can be installed from [GitHub](https://github.com/braunlab-nu/fasano.franceschini.test/) with:
